\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-23 paper.tex
Fix

The process of tracking local coalescences and updating
segments of ancestral material is a core element of
Hudson's seminal simulation simulation
algorithm~\citep{hudson1983testing,kelleher2016efficient},
and the key distinguishing feature between the
``Big'' and ``Little'' ARG stochastic processes
(see Appendix~\ref{sec-big-and-little-arg}).
The ability to \emph{store} the resolved ancestral material
for a sample
in an ARG is also a key distinction between the eARG and gARG
encodings. Because an eARG stores only the graph topology and
recombination breakpoints, there is no way to locally
ascertain the ancestral material without traversing the graph
rootwards from the samples,
resolving the effects of recombination and common ancestor events.

>>>>

The process of tracking local coalescences and updating
segments of ancestral material is a core element of
Hudson's seminal simulation
algorithm~\citep{hudson1983testing,kelleher2016efficient},
and the key distinguishing feature between the
``Big'' and ``Little'' ARG stochastic processes
(see Appendix~\ref{sec-big-and-little-arg}).
The ability to \emph{store} the resolved ancestral material
for a sample
in an ARG is also a key distinction between the eARG and gARG
encodings. Because an eARG stores only the graph topology and
recombination breakpoints, there is no way to locally
ascertain the ancestral material without traversing the graph
rootwards from the samples,
resolving the effects of recombination and common ancestor events.
